---
title: "Brownlows Bets"
author: "Daniella Parra"
date: "Summer 2021"
output: 
  html_document:
    number_sections: true
    toc: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
require(tidyverse)
require(tigerstats)
require(knitr)
source(file = "BrLw.R")
```


<!-- We recommend you use git branches -- create a separate branch for each major section i.e. Introduction, Methods, Results, Inferential Results, and Discussion and Conclusions - leave the YAML block untouched until the final merge where you put in your own name !-->

# Introduction

<!--In this section you explain what you are trying to show.  Where did the data come from?  What is the research or other question you are trying to answer?!-->

 At the first day of class there are 35 students in Math Statistics class and professor Brownlow always proposes this bet to his students "I will wager $2 to your bet of $1 that at least two people in today's class have  the same birthday.  He tells me he has made that bet 637 times so far. Where do you think his profits are? Discuss this in a markdown document
 
Report git commit structure:
There are 3 questions and there should be at least 3 separate commits, at least one dealing with each of the 3 questions.
1. What are the fair odds for a bet on matching birthdays in a 35 person class.
2. For what size class is a 2:1 odds bet fair.
3. How much money would Brownlow be expected to end up with if the bets went as described.

# What are the fair odds  


<!--Decide on your methods:  In this section explain the approach you will take to attack the issue --- how will you decide on a likely estimate of professor Brownlow's earnings or losses after 637 bets. Also explain how you construct a 95% confidence interval about your estimate of his winnings !-->


```{r}
BrLw(35,4.35,637)
```

```{r}
bank=numeric()
for(j in 1:500){

  
bank[j] = BrLw(35,4.35,637)
}
```


```{r}
hist(bank)
```

After rerunning this we can see this is way too broad of a percentage you either win a ton or lose a ton, there is no real middle. 

```{r}
favstats(bank)
sorted <- sort(bank)
print(sorted[12])
print(sorted[488])
```


Here we can see where the min of -181.55 of what you can lose and the max you can win is 134.15. 

We can either win a lot of money or lose a lot more no real middle here. 



# What size of class makes the 2:1 bet fair?  
<!--Explain and display the results of your method of coming up with the estimate of professor Brownlows betting profits!-->

```{r}
BrLw(35,2,637)
```


```{r}
bank=numeric()
for(j in 1:500){

  
bank[j] = BrLw(35,2,637)}
```


```{r}
hist(bank)
```

After running this one a couple of times we can see that you can sit mainly at 200 and not much less than that it will bounce around 200-300. 


```{r}
favstats(bank)
sorted <- sort(bank)
print(sorted[12])
print(sorted[488])
```

Here we can see the minimum we can get is 187, where as before with a 4.35 chance we had a min of -150. 

Our max is also 367 which is a huge jump, but we can also say this chance would give us a comfortable spot around 187 to 367. 

# In the class and payoff as described what is a 95% confidence interval for Brownlow's earnings?
  
<!--Explain and display your method of coming up with a 95% confidence interval of  professor Brownlows winnings (or losings)-->

```{r}
BrLw(35,2,637)
```

```{r}
bank=numeric()
for(j in 1:1000){


bank[j]=BrLw(35,2,637)}
```

```{r}
hist(bank)
```

Here we changed out of 1000, and we can see that this also has a higher chances of being around the 200-300 as well. 


```{r}
favstats(bank)
sorted <- sort(bank)
print(sorted[25])
print(sorted[975])
```

After changing this out of 1000, we can see our min is 160, and our max is 391 not so different from our second charts. 


# Discussion and Conclusion

<!--Discussion and conclusion here.  If professor Brownlow is consistantly making or losing money how could he change his payout so that his profits center on zero?  Also discuss what size his class should be in order to have his current scheme balance at zero profit.!-->


We first had to find out how many people and what kind of percentages we would give for the chances, to figure out the betting and to see the minimum and max we can get for the bets. 

We can see in the first graph with the chances of 4.35, where we go into the negatives if we lose, and don't win much back if we do win. This was a way broader chances that we can just keep loosing and not win much back, the first graphs would be the closest to 0. 

The second graph we can see that if we kept on running it we can see it be more on the 200-300 side, and not very close to zero with the lowest being around 100. 
On the third graph is where we changed out of 500, we do 1000, and got almost the same results of the second graph where we sit around 200-300, while our lowest being 100. 

Overall the one most likely to keep hitting zero first will most definitely be our first graph just because its always leaning more to the left and not really winning much where as our two other graphs are always leaning more to the right even if we don't win much it does not hit down to zero, like the first graph does. 


